---
title: "Lab 3"
author: "Ama Konadu Appau"
date: "`r Sys.Date()`"
output: word_document
---

```{r}
library(tidyverse)
```

Question 1
```{r}
V <- c("Bears", "Lions", "Dolphins", "Eagles", "Bengals")
```
The vector V above is an atomic vector because all the objects in the vector belong to the character strings family.They are homogeneous

Question 2
```{r}
V[3]
```

Question 3
```{r}
V[c(1,3,5)]
```

Question 4
```{r}
V[c(2,3,4,5)]
V[-1]
```

Question 5
```{r}
K <- list( x = 3:7, "never", 43, y = list(10,20,30))
```

The vector K above is  list because it contains objects of different types.It also contains another list y.
The objects are from different families. 
x = 3:7 and 43 are from the famiy of integers,"never" is a character string object and y is an integer list


Question 6
```{r}
length(K)
```

Question 7
```{r}
K[4]
```

Question 8
```{r}
K[1:4]
K
```

Question 9a
```{r}
tribble( ~x,    ~y,    ~w,    ~z,
              210,   300,   220,   180,
              102,   100,   119,   187,
              176,   175,   188,   173,
              87,    95,   91,     94,
              202,   210,  234,    218,
              110,   122,  131,    128,
) -> dt
map_dbl(dt, mean)
```
Question 9b
```{r}
map_dbl(dt, sd)
```

Question 9c
```{r}
dt %>%
  map(sqrt)
```

Question 9d
```{r}
dt %>%
  map(summary)
```











